---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Strativerse (source)

<!-- badges: start -->
[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This is the source of the [Strativerse](http://strativerse.org), as a [Hugo](https://gohugo.io/) site. Changes to this repository are automatically synced to <https://strativerse.org> using [Netlify](https://netlify.com). If you are interested in contributing, I suggest [opening an issue](https://github.com/paleolimbot/strativerse-hugo/issues/new). You can browse the Strativerse at <https://strativerse.org/>, or clone this repository, open in [RStudio](https://rstudio.com/) and use the hacked-together R toolbox to work with objects in tabular form.

```{r}
# these functions are in the .Rprofile and should 
# be loaded when you open the project
sv_records()
sv_features()
sv_publications()
```




